Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-06-14 cmsb22.tex
Stuff related to mpbn

@@

%%% The proposed method and mpbn %%%
\revise{The first observation is that for 27 of the 33 models (more than 78\%), mpbn did not give any answer because it recognized that these models are not locally-monotonic.
For 6 of the 33 models where mpbn returned the answers, mpbn and Trappist are comparable in computation time.
Along with the fact that mbpn can handle only locally-monotonic models and Trappist can handle general models, it is less insightful to further compare between them.
Hence, we focus on only comparisons between PyBoolNet and Trappist in the following observations.}

>>>>

\revise{It is worth noting that there has been a recent method~\cite{DBLP:conf/ictai/ChevalierFPZ19} for computing minimal trap spaces, which avoids the prime-implicants computation.
This method has been implemented in the tool mpbn\footnote{\url{https://github.com/bnediction/mpbn}} demonstrated in~\cite{Paulev2020} for handling medium-sized models from the literature and very large synthetic models (up to 100,000 nodes).
However, this method is only applicable for \emph{locally-monotonic} Boolean models, whereas the prime-implicants based method~\cite{klarner2015computing} is applicable for general Boolean models (i.e.. including both locally-monotonic and non-locally-monotonic Boolean models).
The study~\cite{DBLP:journals/tcs/NoualRS13} highlights the need of non-locally-monotonic Boolean models in both biological and theoretical aspects.
Hence, it is still necessary to develop efficient methods for computing minimal trap spaces of large-scale general Boolean models.
}

@@

%%% The proposed method and mpbn %%%
\revise{The first observation is that for 26 of the 33 models (more than 78\%), mpbn did not give any answer because it recognized that these models are not locally-monotonic.
For 6 of the 33 models where mpbn returned the answers, mpbn and Trappist are comparable in computation time.
Along with the fact that mbpn can handle only locally-monotonic models and Trappist can handle general models, it is less meaningful to further compare between them.
Hence, we focus on only comparisons between PyBoolNet and Trappist in the following observations.}
